\documentclass[14pt]{article)
\begin{document}
\begin{center}\begin{small}MAKERERE UNIVERSITY\end{small}\end{center}

\begin{center}\begin{small}COLLEGE OF COMPUTING AND INFORMATION SCIENCES\end{small}\end{center}

\begin{center}\begin{small}SCHOOL OF COMPUTING AND INFORMATION SCIENCES\end{small}\end{center}

\begin{center}\begin{small}DEPARTMENT OF COMPUTER SCIENCE\end{small}\end{center}

\begin{center}\begin{small}BACHELOR OF SCIENCE INCOMPUTER SCIENCE\end{small}\end{center}

\begin{center}\begin{small}COURSE NAME: RESEARCH METHODOLOGY\end{small}\end{center}

\begin{center}\begin{small}COURSE CODE: BIT 2207\end{small}\end{center}

\begin{center}\begin{small}NAME: MBABAZI SARAH\end{small}\end{center}

\begin{center}\begin{small}REG NO: 15/U/7570/EVE\end{small}\end{center}

\begin{center}\begin{small}ST NO: 215007476\end{small}\end{center}
\title{THE REPORT ON HOW TO MAKE PILLAU}
\maketitle

 Pillau is the best meal I have ever had in my life, I like it so much because its taste and delicious and everyone loves to taste it. Pillau can be prepared using different ingredients like chicken, beef, goat and meat.

\section{How to prepare a beef flavor.}

Am going to explain how I can prepare Pillau with beef .I first cut the beef into small pieces so that they can be delicious in my rice, I wash it and put it in the saucepan, I put in one big onion ”baganda onions”, I put in salt ,I light my charcoal stove and then I put on .
I keep on stirring in it until the water has dried, I add in cooking oil and salt and keep on stirring until it turns brown, I add in another onion until they also turn brown I put in tomatoes, green paper and other ingredients, after they are all ready, I put in Pillau masala and royco and then I add in water.

\section{How to prepare rice.}

If I have  unsorted rice, I first remove the  unwanted  staff like stones and  some rice covers then I put it  in a dish or a container and wait for the water to boil.

\section{How to come up with pillau.}

After the water boiled, i put in rice then keep on stirring until the all the water is gone, after I reduce on the charcoal, put on some ash and then leave the rice to dry and stay hot.
My pillau is ready to be served, I start serving the people with the delicious meal which looks so taste and looks good.

\section{Conclusion.}

I suggest that that everyone should   try and test pillau because it’s so delicious and fantastic.it looks good, has a nice aroma and wow! It’s the best aroma ever. The moment you spot it there and then you start salivating so everyone should try it out.

\end{document}